Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
fixes

As said before, the web-based source code analysis service \emph{Better Code
Hub} (BCH) is used to collect the maintanability reports of the refactorings of
each project. Table~\ref{tab:guidelines} presents the 10 guidelines
proposed by BCH's authors for delivering software that is easy to maintain~\cite{Visser:2016:OREILLY}. All guidelines are computed in the same evaluation by
BCH. During each guideline evaluation, the tool determines the compliance towards
one guideline by establishing limits for the percentage of code allowed to be in
each of the $4$ risk severity levels (\emph{low risk}, \emph{medium risk}, \emph{high risk}
and \emph{very high risk}). If the project does not violate the thresholds, then it
is compliant with the guideline. These thresholds are calibrated by BCH using
their own data/experience --- open-source and closed software systems. If a
project is compliant with a guideline, it means that it is at least $65\%$
better than the software used by BCH to calculate the thresholds\footnote{Check
the answer to \emph{How can I adjust the threshold for passing/not passing a
guideline?} at https://bettercodehub.com/docs/faq (Accessed on \today{})}.

@@

\emph{Units} are the smallest groups of code that can be maintained and executed
independently~\cite{Visser:2016:OREILLY}. McCabe~\cite{1702388} is a software
metric that calculates the number of linearly independent paths of the source
code. BCH uses this metric to measure the number of branch points in the
\emph{Write Simple Units of Code} guideline. The bar represents the top 30 of
units that violates the guideline, sorted by severity, which is indicated by the
colors of the checkboxes. The green bar represents the number of compliant
branch points per unit (\emph{at most 5}), i.e., the units are compliant with
ISO 25010~\cite{iso:2011}. Yellow, orange and red bars represent units that do
not comply with medium (\emph{above 5}), high (\emph{above 10}) and very high
(\emph{above 25}) severity levels. In the bar, there are marks that pinpoint the
compliance thresholds for each severity level. If the green mark is somewhere
in the green bar it means it is compliant with a low level of severity.

>>>>

As said before, the web-based source code analysis service \emph{Better Code
Hub} (BCH) is used to collect the maintanability reports of the refactorings of
each project. Table~\ref{tab:guidelines} presents the $10$ guidelines proposed
by BCH's authors for delivering software that is not difficult to
maintain~\cite{Visser:2016:OREILLY}. During each guideline evaluation, the tool
determines the compliance towards one guideline by establishing limits for the
percentage of code allowed to be in each of the $4$ risk severity levels
(\emph{low risk}, \emph{medium risk}, \emph{high risk} and \emph{very high
risk}). If the project does not violate the thresholds, then it is compliant
with the guideline. These thresholds are calibrated by BCH using their own
data/experience --- open-source and closed software systems. If a project is
compliant with a guideline, it means that it is at least $65\%$ better than the
software used by BCH to calculate the thresholds\footnote{Check the answer to
\emph{How can I adjust the threshold for passing/not passing a guideline?} at
https://bettercodehub.com/docs/faq (Accessed on \today{})}.

@@

\emph{Units} are the smallest groups of code that can be maintained and executed
independently~\cite{Visser:2016:OREILLY}. McCabe~\cite{1702388} is a software
metric that calculates the number of linearly independent paths of the source
code. BCH uses this metric to measure the number of branch points in the
\emph{Write Simple Units of Code} guideline. The bar at the bottom of the figure
represents the top $30$ units that violates the guideline, sorted by severity,
The violation severities are indicated using colors, and there is a legend to
help interpreting the colors. The green bar represents the number of compliant
branch points per unit (\emph{at most 5}), i.e., the units are compliant with
ISO 25010~\cite{iso:2011}. Yellow, orange and red bars represent units that do
not comply with medium (\emph{above 5}), high (\emph{above 10}) and very high
(\emph{above 25}) severity levels. In the bar, there are marks that pinpoint the
compliance thresholds for each severity level. If the green mark is somewhere
in the green bar it means it is compliant with a low level of severity.
